### 2023-04-20 state-resilience.tex
up

\problemx{$d$-VASS zero-reachability}
{VASS $V=(Q,T)$, $p(\textbf{u}) \in Q \times \N^d$}
{$\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$? \\}

@@

\begin{samepage}
\problemx{Zero-reachability}
{A Reset $d$-VASS $V=(Q,T)$, $q(\textbf{u}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{u}) \to^* p(\textbf{0})$? \\}
\end{samepage}
%
\alain{ce qui précède est inutile}
\fi
~ of zero-reachability in Reset $d$-VASS.
%
We reduce the zero-reachability problem to the problem of deciding whether a control-transition is live, that is, whether it is always ,
which we then reduce to {\sc State-resilience}.
A control-transition $t$ of a Reset $d$-VASS is {\em live} in a configuration $r(\textbf{w})$ if for each $q(\textbf{v}) \in \post^*(r(\textbf{w}))$ there exists a 
%\alain{mélange de s et (p,u)}
 $p(\textbf{u})$ with $q(\textbf{v}) \to^* p(\textbf{u})$ such that $t$ is enabled in $p(\textbf{u})$. We say the whole Reset $d$-VASS is live if all its control-transitions are
live. This leads to the following problem.

@@

\mathieu{Quelque chose de plus à dire sur la charactérisation?}

VASS for instance are $\uparrow \post^*$-effective WSTS \cite{DBLP:journals/corr/abs-2108-00889}. 
\iffalse

@@

\begin{proof}
Consider Reset $d$-VASS
with $\Safe$ % where  $ \textbf{0} = 0^d \in \mathbb{N}^d$ 
	containing only the
		configurations in $Q \times \{ \textbf{0} \}$
	where $\textbf{0} = \min(\mathbb{N}^d)$ %$0$ 
% \alain{tu n'as pas le doit d'écrire $0$ sans explication}
and $\Bad = \mathbb{N}^d \setminus \Safe$.
It follows in this case that
{\sc State-resilience} 
% \alain{écris toujours pareil les expressions choisies comme state-resilience}
is equivalent 
to the problem of whether 
% $0$  can be visited infinitely often. 
it is possible to visit infinitely often configurations with every vector having its value equal to $0$.
\alain{incompréhensible, explique}
Indeed, from such a configuration, then the next step is either also such a configuration, either it is in $\Bad$, in which case, we know it is possible to reach such a configuration again. Hence we construct a sequence 
$(q_i ({\textbf{v}_{i}}) )_{i\in\N}$ 
such that for all $i\in\N$ 
$\exists j \in \N$, $j>i$, s.t. ${\textbf{v}_j} = \textbf{0}$.
% Since reachability of $0$ is undecidable for Reset VASS, we conclude.
Hence the undecidability.
\end{proof}

>>>>

\iffalse
\problemx{$d$-VASS zero-reachability}
{VASS $V=(Q,T)$, $p(\textbf{u}) \in Q \times \N^d$}
{$\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$? \\} 
\fi

@@

\begin{samepage}
\problemx{Zero-reachability}
{A Reset $d$-VASS $V=(Q,T)$, $q(\textbf{u}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{u}) \to^* p(\textbf{0})$? \\}
\end{samepage}
%
\alain{ce qui précède est inutile}
\fi
~ of {\em zero-reachability} in Reset $d$-VASS, which consists in, given a
Reset $d$-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$,
deciding whether $\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$.
%
We reduce the zero-reachability problem to the problem of deciding whether a control-transition is live, that is, whether it is always ,
which we then reduce to {\sc State-resilience}.
A control-transition $t$ of a Reset $d$-VASS is {\em live} in a configuration $r(\textbf{w})$ if for each $q(\textbf{v}) \in \post^*(r(\textbf{w}))$ there exists a 
%\alain{mélange de s et (p,u)}
 $p(\textbf{u})$ with $q(\textbf{v}) \to^* p(\textbf{u})$ such that $t$ is enabled in $p(\textbf{u})$. We say the whole Reset $d$-VASS is live if all its control-transitions are
live. This leads to the following problem.

@@

% \mathieu{Quelque chose de plus à dire sur la charactérisation?}

More concretely,
VASS for instance are $\uparrow \post^*$-effective WSTS \cite{DBLP:journals/corr/abs-2108-00889}. 
\iffalse

@@

\begin{proof}
Consider Reset $d$-VASS
with $\Safe$ % where  $ \textbf{0} = 0^d \in \mathbb{N}^d$ 
	containing only the
		configurations in $Q \times \{ \textbf{0} \}$
	where $\textbf{0} = \min(\mathbb{N}^d)$, %$0$ 
% \alain{tu n'as pas le doit d'écrire $0$ sans explication}
and $\Bad = \mathbb{N}^d \setminus \Safe$.
It follows in this case that
{\sc State-resilience} 
% \alain{écris toujours pareil les expressions choisies comme state-resilience}
is equivalent 
to the problem of whether 
% $0$  can be visited infinitely often. 
it is possible to visit infinitely often configurations with every vector having all values equal to $0$.
% \alain{incompréhensible, explique}
Indeed, from such a configuration, then the next step is either also such a configuration, either it is in $\Bad$, in which case, we know it is possible to reach such a configuration again. From this we know there exists a sequence 
$(q_i ({\textbf{v}_{i}}) )_{i\in\N}$ 
such that for all $i\in\N$ 
$\exists j \in \N$, $j>i$, s.t. ${\textbf{v}_j} = \textbf{0}$.
% Since reachability of $0$ is undecidable for Reset VASS, we conclude.
Hence the undecidability.
\end{proof}
